Crowdy: Social Crowd Visualization

### 2011-03-01 docs/crowdy_gui.tex
Merged some changes from Zhiyuan
did spellchecking and started implementation

\begin{document}

@@

\numberofauthors{1} 
\author{
    \alignauthor Jeffrey McGee, Zhiyuan Cheng, Chiao-Fang Hsu, Pratheek
    Kumar Akireddy \\
    \affaddr{Department of Computer Science and Engineering, Texas A\&M
    University} \\
    \affaddr{ College Station, TX 77845 USA} \\
    \email{jeffamcgee@gmail.com, chengzhy@gmail.com, drakihsu@cse.tamu.edu,
    pka293@cse.tamu.edu}
}

\maketitle
\begin{abstract}
Microblogging systems have provided society with a more transparent channel
for information distribution. Each individual is empowered to spread news
and build their social networks. With the freedom of information generation,
the issue now is identifiying, organizing, visualizing useful information.
For this project, we want to design an user interface that takes
both usefulness and usability into consideration. Our system will
adapt to different types of users and display the crowds that form in a specific
period of time as well as the topics discussed by the crowd from Twitter. The
interface should both optimize the user experience and system speed. For
evaluation, we will design some user study or inspection procedures in order to
test the efficiency, effectivness, and satisfaction of this system to our
poential users.
\end{abstract}

@@

In addition, with the nature of the temporal massive data, we do not expect our
users to remember where to find the crowd/topic of interest that the user just
encountered. We want to provide a Workspace panel so to release the stress on
the memory requirment from the user.

@@

In the other study based on the previous one, K. Y. Kamath et
al\cite{kamath2011transient}, they add another salient feature - a novel crowd
tracking and evolution approach for linking crowds across time periods. Unlike
the more static and long-lived group-based membership offered on many social
networks their goal is to support the discovery of organic and highly-temporal
group affiliation, which they refer to as ``transient crowds''. A transient
crowd according to them is a potentially short-lived ad-hoc collection of users
bound together by some common thread – which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in “crowdy” in a
similar fashion.

@@

\section{Implementation}

>>>>

\pdfpagewidth 8.5in
\pdfpageheight 11in

@@

\numberofauthors{1} 
\author{
    \alignauthor Jeffrey McGee, Zhiyuan Cheng, Chiao-Fang Hsu, Pratheek
    Kumar Akireddy \\
    \affaddr{Department of Computer Science and Engineering, Texas A\&M
    University} \\
    \affaddr{ College Station, TX 77845 USA} \\
    \email{jeffamcgee@gmail.com, zcheng@cse.tamu.edu, drakihsu@cse.tamu.edu,
    pka293@cse.tamu.edu}
} 
\begin{document}

\maketitle
\begin{abstract}
Microblogging systems have provided society with a more transparent channel
for information distribution. Each individual is empowered to spread news
and build their social network. With the freedom of information generation,
the issue now is identifying, organizing, and visualizing useful information.
For this project, we want to design an user interface that takes
both usefulness and usability into consideration. Our system will
adapt to different types of users and display the crowds that form in a specific
period of time as well as the topics discussed by the crowd from Twitter. The
interface should both optimize the user experience and system speed. For
evaluation, we will design a user study to
test the efficiency, effectiveness, and satisfaction of this system to our
potential users.
\end{abstract}

@@

In addition, with the nature of the temporal massive data, we do not expect our
users to remember where to find the crowd/topic of interest that the user just
encountered. We want to provide a Workspace panel so to release the stress on
the memory requirement from the user.

@@

In the other study based on the previous one, K. Y. Kamath et
al\cite{kamath2011transient}, they add another salient feature - a novel crowd
tracking and evolution approach for linking crowds across time periods. Unlike
the more static and long-lived group-based membership offered on many social
networks their goal is to support the discovery of organic and highly-temporal
group affiliation, which they refer to as ``transient crowds''. A transient
crowd according to them is a potentially short-lived ad-hoc collection of users
bound together by some common thread – which can be communication-based,
location-based or interest based. We are inspired by this idea of formation and
detection of crowds. We try to implement detection of crowd in “Crowdy” in a
similar fashion.

@@

\section{Implementation}
The system is designed to run in a user's web browser.
As a result, we choose to use some fairly standard web tools to implement the system.
The system that we are building the user interface on top of exposes a RESTful API.
To retrieve data, our system makes an HTTP GET request to the server.
The server returns data in the JSON format, which is easy to decode in Javascript.

CherryPy
Jinja

jQuery
Simile Timeline
Google Maps API
